Supplementary Information

### 2023-09-08 supplement.Rmd
effect size calcs

Focusing on HMM models with 5 latent states (which is the optimal number for the HMM-full model) we estimated the investors' policy in each of the five latent states assuming a discretised Gaussian response function as highlighted in the previous section. Each latent state was associated with a distribution over trustee actions. The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher "trustworthiness".

>>>>

Focusing on the HMM-full models with 5 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section. Each latent state was associated with a distribution over trustee actions. The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher mean percentage return.
